Digital Analysis of Paintings

### 2014-05-03 paper.tex
Add introduction for brushstrokes.

\section{Texture Analysis}
Paintings are somewhat unlike the normal subject for image processing, whilst
most images are either simple two dimensional images, or two dimensional slices
of a three dimensional object. Paintings often thought of as two dimensional,
but with many paint types these paintings become three dimensional.

@@

>>>>

\section{Texture Analysis}\label{sec:texture}
Paintings are somewhat unlike the normal subject for image processing, whilst
most images are either simple two dimensional images, or two dimensional slices
of a three dimensional object. Paintings often thought of as two dimensional,
but with many paint types these paintings become three dimensional.

@@

The ideal technique for analysing a painting digitally is to be able to extract
brushstrokes from the painting and be able to analyse them based on their
shape, colour and where on the painting different types of stroke were made.

This is a very difficult task, it may be easy for a human non-expert to view a
painting and roughly estimate where the surface brushstrokes are, implying that
an expert may be able to tell far more from a detailed view of the painting,
including multispectral imaging using X-rays.

For a computer to do this is a very intensive and complex task. As discussed
in section~\ref{sec:texture} is can be easy to view the texture of an image and
even to be able to pull out some information about the texture of brushstrokes.
But actually segmenting these brushstrokes for extraction quickly is a
different story.

This section will look into some of the research which has been attempting to
extract brushstrokes from paintings for the purposes of identification and
authentication of artwork. However, because this field is relatively narrow,
some exploration into extraction of brushstrokes in calligraphy will also be
considered as the fields have some overlap.
